---
output:
  word_document:
    reference_docx: "template - Briefing note.docx"

---



```{r setup, include=FALSE, cache=FALSE}

knitr::opts_chunk$set(echo = TRUE)
library(dplyr)

wd <- getwd()


```

```{r include=FALSE, cache=FALSE}

# Inputs - Change these for each new output
author<-"Your Name"
extension<-"#99999"
current_quarter <- 2
current_year <- 2017
release_date <- "4 October 2017"


# The next line calculates all the numbers and saves them as econ_data.txt. Comment it out avoid redownloading data unnecceserily.

#source('calculate_number_for_gdp_report.r')

#Load up the economic data
econ_data<- read.csv("econ_data.txt",colClasses=c("character","character","character","character"))

#Asign the variables
scot_growth <- econ_data %>%
  filter(Time=="Short term", 
         Sector=="GDP") %>%
  select(Scotland)

uk_growth <- econ_data %>%
  filter(Time=="Short term", 
         Sector=="GDP") %>%
  select(UK)

service_growth <- econ_data %>%
  filter(Time=="Short term",
         Sector=="Services") %>%
  select(Scotland)

production_growth <- econ_data %>%
  filter(Time=="Short term", 
         Sector=="Production") %>%
  select(Scotland)

construction_growth <- econ_data %>%
  filter(Time=="Short term", 
         Sector=="Construction") %>%
  select(Scotland)

scot_year_growth <- econ_data %>%
  filter(Time=="Medium term", 
         Sector=="GDP") %>%
  select(Scotland)

uk_year_growth <- econ_data %>%
  filter(Time=="Medium term", 
         Sector=="GDP") %>%
  select(UK)

scot_gdp_per_pop <- econ_data %>%
  filter(Time=="Medium term", 
         Sector=="GDP per head") %>%
  select(Scotland)

uk_gdp_per_pop <- econ_data %>%
  filter(Time=="Medium term", 
         Sector=="GDP per head") %>%
  select(UK)

scot_4q <- econ_data %>%
  filter(Time=="4Q", 
         Sector=="GDP") %>%
  select(Scotland)

uk_4q <- econ_data %>%
  filter(Time=="4Q", 
         Sector=="GDP") %>%
  select(UK)

# Calculate which was the last quarter
prev_quarter_number<-current_quarter-1
if(prev_quarter_number==0){prev_quarter_number <- 4}

# Make some nice formatted objected to insert into text
this_quarter<- paste("Q",current_quarter,sep="")
last_quarter<- paste("Q",prev_quarter_number,sep="")

name_quarter <- function(quarter){
  if(quarter==1){
    paste("first")
  } else if(quarter==2){
    paste("second")
  } else if(quarter==3){
    paste("third")
  } else if(quarter==4){
    paste("fourth")
  } else {
    paste("###ERROR IN TEXT QUARTER")
  }
}

text_quarter <- name_quarter(current_quarter)
text_previous <- name_quarter(prev_quarter_number)

if(current_quarter==1){
   previous_quarters_year<-current_year-1
} else {
  previous_quarters_year<-current_year
}

last_year <- current_year - 1

#Translate quarter to month range
if(current_quarter==1){
  month_range<-"January to March"
} else if(current_quarter==2){
  month_range<-"April to June"
} else if(current_quarter==3){
  month_range<-"July to September"
} else if(current_quarter==4){
  month_range<-"October to December"
} else {
  text_quarter<-"ERROR IN month_range"
}

describe_growth <- function(percentage){
  if (percentage=="0.0" || percentage == "+0.0" || percentage == "-0.0"){
    paste("remained flat (0.0% growth)",sep="")
    } else if (as.numeric(percentage) > 0 ){
    paste("grew by " , format(as.numeric(percentage),nsmall=1),"%",sep="")
    } else if (as.numeric(percentage) < 0 ){
    paste("contracted by ",
          format(abs(as.numeric(percentage)),nsmall=1),"%",sep="")
    } else {
    paste("ERROR IN DIRECTION CODING!!!")
    }
}

```
#### USE THIS AS A HEADER AND PAGE BREAK

First line of report.

# REPORT NAME FOR THE DATE `r paste(current_year, this_quarter)`

# Purpose

###WHAT IS THE PURPOSE OF THIS REPORT

# Priority

###WHAT IS THE PRIORITY? The statistics will be published on `r release_date` at 09:30. 

# Background

###THIS REPORT DESCRIBES WHAT HAPPENED in the period from `r paste(month_range, current_year)`.

# Key points

###EXAMPLE OF TEXT AND CODE IN `r text_quarter` quarter of `r current_year` DESCRIBE CHANGE **`r describe_growth(scot_growth)`**. SECOND EXAMPLE **UK was `r paste(uk_growth %>% as.numeric() %>% format(nsmall=1),"%", " in ",current_year," ",this_quarter,sep="")`**.


###ANOTHER EXAMPLE (i.e. `r paste(current_year, this_quarter,"vs",last_year,this_quarter)`), the Scottish economy `r describe_growth(scot_year_growth)`. Equivalent UK growth was `r uk_year_growth %>% as.numeric() %>% format(nsmall=1)`%.

# Conclusion

###**DESCRIBE WHO NEEDS TO NOTE THIS. The publication will be released on `r paste(weekdays(as.Date(release_date,"%d %B %Y")), release_date)` **

#`r author`
`r extension`

##`r format(as.Date(release_date,"%d %B %Y") - 1, format="%d %B %Y")`

#### PRE-RELEASE STATISTICS - **OFFICIAL SENSITIVE** until `r release_date` at 09:30

# INSERT COPY LIST HERE